Effective multi-body SU($N$)-symmetric interactions of ultracold fermionic atoms on a 3-D lattice

### 2019-02-08 multi_body_interactions/papers/theory/reviews_NJP/referee_1_response.tex

  \green{Second, (5) is only the first term in a low-energy expansion
    of two-body interactions in effective field theory, which
    generally includes additional terms containing derivatives of
    field operators.  Derivative terms correspond to the dependence of
    two-body scattering on the relative momentum $k$ of particles
    involved, with $k\to0$ in the zero-energy limit.  In the present
    case of $s$-wave scattering, the leading dependence of the
    two-body interaction Hamiltonian on the relative momentum $k$ can
    be captured by use of an energy-dependent pseudo-potential, which
    amounts to using a $k$-dependent effective scattering length [46].
    This effective scattering length can be determined by expanding
    the $s$-wave collisional phase shift in powers of the relative
    momentum $k$ [45, 47].  Details of this expansion will depend on
    the characteristic length scale of finite-range interactions.  In
    our work, these corrections to (5) will be relevant only for the
    calculation of two-body interaction energies, appearing at third
    order in the coupling constants $G_X$.  As we are primarily
    interested in $M$-body interactions for $M\ge3$, we defer this
    calculation to Appendix D.  We note that our approach of using an
    unregularized contact potential, renormalizing coupling constants,
    and separately accounting for momentum-dependent scattering is
    essentially the same as that used for similar calculations in
    refs.~[35--37].  While this approach does not provide insight into
    the microscopic nature of atomic interactions, it is suitable for
    the phenomenological description of these interactions, and
    particular for our eventual development of a low-energy effective
    theory.}

  Expanding on our use and method of renormalization, we have changed
  the following text in section III B (page 12, line 15):

@@

  \red{In general, the sums over excited states in the loop diagrams
    of (15) will diverge [35], which implies the need to renormalize
    the coupling constants in our theory.  Even if these diagrams do
    not diverge, we would like to express the effective two-body
    interactions in terms of net, physically observable two-body
    coupling constants as on the right-hand side of (15), rather than
    in terms of long sums at all orders of the bare coupling
    constants.  We therefore renormalize our coupling constants by
    introducing counter-terms $\tilde G_X$ into the effective
    interaction Hamiltonians via $G_X\to G_X+\tilde G_X$.  The values
    of these counter-terms are fixed by enforcing that $G_X$ is equal
    to the net two-body interaction strength.}

  with:

  \green{On physical grounds, the net effective two-body interaction
    must clearly be finite, but individual sums over the excited
    states in loop diagrams of (15) may generally diverge [35].  These
    divergences ultimately appear due to our use of effective field
    theory to describe inter-atomic interactions in (2), (5), and (7),
    rather than a detailed microscopic description of two-atom
    scattering.  Divergences of this sort are a generic feature of
    field theories, and can be dealt with using standard techniques
    such as renormalization.  We therefore renormalize our coupling
    constants by introducing counter-terms $\tilde G_X$ into the
    interaction Hamiltonian.}

  We further discuss our method of renormalization later in point
  \ref{pt:renormalization}.

@@

  We have also modified the wording in our discussion of corrections
  to Eqs.~(2) and (5) at the end of section III B, replacing the text
  (page 13, line 24):

  \red{Second, the overview we provided in section II, and
    consequently our result in (17), neglects the effect of
    momentum-dependent two-body scattering. When the effective range
    of momentum-dependent interactions is comparable to the scattering
    lengths $a_X$, as is the case for ultracold ${}^{87}$Sr, these
    interactions are third order in the coupling constants $G_X$. Just
    as the $\O\p{G^2}$ counter-terms do not affect $M$-body
    interactions until next-to-leading order (NLO), the $\O\p{G^3}$
    momentum-dependent interactions do not come into play until next-
    next-leading order (NNLO).}

  by:

  \green{Finally, our result in (17) neglects the effect of
    momentum-dependent two-body scattering.  When the effective range
    of interactions is comparable to the scattering lengths $a_X$, as
    is the case for ultracold ${}^{87}$Sr, these momentum-dependent
    effects are third order in the coupling constants $G_X$.  Just as
    the $\O\p{G^2}$ counter-terms do not affect $M$-body interactions
    until next-to-leading order (NLO), the $\O\p{G^3}$
    momentum-dependent terms do not come into play until
    next-next-leading order (NNLO).}

@@

  We hope these changes and discussions help clarify our treatment of
  two-body $s$-wave interactions, in particular addressing any
  subtleties and potential concerns as soon as we introduce a two-body
  interaction Hamiltonian.

\item Concerning corrections to many-body energy eigenstates in our
  effective theory:

@@

  \blue{(v) On page 10: For the sentence ``Finally, the effective
    theory involves no corrections to the many-body energy
    eigenstates.'' the referee can again only guess, what the authors
    would like to express, but as it is written it is just plain
    wrong. The states between the non-interacting and the interacting
    theory are connected by a unitary transformation and are therefore
    not identical to the non-interacting ones. }

  We thank the referee for pointing out a subtlety that we need to
  clarify about effective theories constructed with a Schrieffer-Wolff
  transformation.  Between the non-interacting Hamiltonian $H_0$, the
  interacting Hamiltonian $H = H_0 + H_{\t{int}}$, and the effective
  Hamiltonian $H_{\t{eff}}$ constructed from $H$ with a unitary
  transformation, there are different sets of energies and eigenstates
  to keep track of.

  To help clarify the relationship between these different
  Hamiltonians, their eigenstates, and spectra, we have re-written our
  opening to section III, replacing the first two paragraphs (page 8,
  line 36):

@@

  \red{As the bare two-body Hamiltonian $H_{\t{int}}$ is not diagonal
    with respect to single-particle motional states, the problem of
    determining many-body spectra and eigenstates nominally involves
    all motional degrees of freedom of the atoms involved.  If we are
    interested in addressing internal atomic states at zero
    temperature, however, in principle we need only to consider the
    motional ground state associated with each many-body internal
    atomic state.  We can then ignore all excited motional states, as
    they will be neither thermally occupied nor externally
    interrogated.  This procedure makes the many-body problem more
    tractable by greatly reducing the dimensionality of the relevant
    Hilbert space.}

  \red{We denote the space of all internal states of atoms in
    single-particle, non-interacting (multi-particle, interacting)
    motional ground states by $\H_{\t{ground}}^{\t{single}}$
    ($\H_{\t{ground}}^{\t{multi}}$).  For sufficiently weak
    interactions, one can construct a unitary transformation $U$
    acting on the full many-body Hilbert space which rotates
    $\H_{\t{ground}}^{\t{multi}}$ into $\H_{\t{ground}}^{\t{single}}$
    [43].  The unitary $U$ can then be used to construct an {\it
      effective Hamiltonian} $H_{\t{int}}^{\t{eff}}$ on
    $\H_{\t{ground}}^{\t{single}}$ that reproduces the spectrum of
    $H_{\t{int}}$ on $\H_{\t{ground}}^{\t{multi}}$, namely
    $H_{\t{int}}^{\t{eff}}=UH_{\t{int}}U^\dag$.  This method for
    constructing an effective theory is commonly known as the
    Schrieffer-Wolff transformation, named after the authors of its
    celebrated application in relating the Anderson and Kondo models
    of magnetic impurities in metals [44].}

  by:

  \green{The net Hamiltonian $H = H_0 + H_{\t{int}}$ for interacting
    AEAs on a lattice is not diagonal with respect to single-particle
    motional state indices (e.g.~$n\in\mathbb{N}_0^3$).  The problem
    of determining interacting atoms' orbital excitation spectrum
    therefore nominally involves all atomic motional degrees of
    freedom.  At zero temperature, however, each orbital state of a
    collection of interacting atoms is associated with a single
    motional ground state.  In order to compute an orbital excitation
    spectrum at zero temperature, in principle we need to identify
    these motional ground states.  We can then ignore all excited
    motional states, which will be neither thermally occupied nor
    externally interrogated.  Such a procedure would drastically
    reduce the dimensionality of the Hilbert space necessary to
    describe the atoms, thereby greatly simplifying any description of
    the atoms' orbital spectrum and internal (i.e.~nuclear and
    orbital) dynamics.  In practice, however, identifying the motional
    ground states of interacting atoms and writing down a Hamiltonian
    restricted to this subspace is a very difficult process to carry
    out analytically.}

@@

  We have also modified the particular text pointed out by the
  referee, changing (page 10, line 19):

@@

  \red{Finally, the effective theory involves no corrections to the
    many-body energy eigenstates.  Including such corrections would
    invalidate the effective theory, which preserves the eigenstates
    of the non-interacting Hamiltonian $H_0$ on
    $\H_{\t{ground}}^{\t{single}}$.}

  to:

  \green{Finally, the effective theory involves no corrections to the
    non-interacting many-body energy eigenstates; the purpose of
    constructing the effective Hamiltonian
    $H_{\t{eff}} = H_0 + H_{\t{int}}^{\t{eff}}$ is to reproduce, on
    the known eigenstates of the non-interacting Hamiltonian $H_0$
    within $\H_{\t{ground}}^{\t{single}}$, the spectrum of the
    interacting Hamiltonian $H = H_0 + H_{\t{int}}$ on
    $\H_{\t{ground}}^{\t{multi}}$.  ``Correcting'' the eigenstates of
    the non-interacting Hamiltonian $H_0$ on
    $\H_{\t{ground}}^{\t{single}}$ thus invalidates the effective
    theory.}

@@

  We hope that these changes clarify subtleties of the
  Schrieffer-Wolff transformation, and in particular the fact that the
  effective Hamiltonian $H_{\t{eff}}$ has the spectrum of the
  interacting Hamiltonian $H$ on the eigenstates of the
  non-interacting Hamiltonian $H_0$.

\item Concerning:

  \blue{In addition, the is also an important scientific question. The
    authors use renormalization of the theory by adding counter terms
    to remove the diverging contributions. This approach might provide
    the correct result however a microscopic derivation and motivation
    based on the pseudo-potential would be certainly help to justify
    this approach.}

  We agree with the referee that a microscopic derivation of our
  effective theory based on a regularized pseudo-potential would
  provide additional insights, but respectfully disagree that doing so
  is worthwhile for our manuscript.  Microscopic treatment of
  interactions is generally a difficult task; we do not know of any
  analytical descriptions of even {\it two}-body interactions of atoms
  on a lattice (as exist e.g.~in the case of a harmonic trap,
  considered in
  ref.~[\href{https://link.springer.com/article/10.1023\%2FA\%3A1018705520999}{53}]),
  nevermind multi-body interactions that appear in an effective theory
  of the two-body case.  Effective field theory and renormalization,
  meanwhile, are standard and powerful tools for studying interacting
  quantum systems.  These tools are therefore well-suited to our goal
  at hand: to interpret the results of experiments exhibiting
  signatures of multi-body interactions, and build towards the use of
  such experiments to perform interesting quantum simulations.  We
  discussed our use of effective field theory and renormalization in
  our response to point \ref{pt:pseudo-potential}, commenting on our
  particular choice of methods in a pair new sentences inserted
  between Eqs.~(5) and (6):

  \green{We note that our approach of using an unregularized contact
    potential, renormalizing coupling constants, and separately
    accounting for momentum-dependent scattering is essentially the
    same as that used for similar calculations in refs.~[35--37].
    While this approach does not provide insight into the microscopic
    structure of inter-atomic interactions, it is suitable for the
    phenomenological description of these interactions, and particular
    for our eventual development of a low-energy effective theory.}

  We hope that the referee understands our position on this matter,
  and does not consider a microscopic treatment of interactions to be
  compulsory for the publication of our manuscript.

\item Concerning the diagram in Eq.~(22):

  \blue{The referee tried to follow the authors approach, but was
    stuck with the following two problems:}

  \blue{(1) It is unclear to the referee, why the diagram in Eq.(22)
    converges. For large n and m motional state reduces to free
    particles with energy $\sim$ n\^{}2 and m\^{}2 as the energy is
    much higher than the lattice. In addition, the overlap K become a
    constant. Then, a dimensional analysis shows that this term
    diverges logarithmically. It is a significant short coming of the
    manuscript that the authors fail to provide a detailed discussion
    of potential diverging terms. Therefore, it is unclear to the
    referee, whether the chosen approach is well defined.}

  \label{pt:divergence}

  We thank the referee for their careful consideration of our theory,
  for pointing out a potential concern about divergences.  The
  argument for a divergence in our theory essentially concerns a
  quantity in Eq.~(30) on page 16:
  \begin{align*}
    \alpha_3^{(3)} \equiv \sum_{\substack{\ell+m>0\\\ell+n>0}}
    \f{K_{\ell m} K^m_n K_{\ell n}}{\p{E_\ell+E_m}\p{E_\ell+E_n}},
  \end{align*}
  for $\ell,m,n\in\mathbb{N}_0^3$ with
  e.g.~$\ell\equiv\p{\ell_\x,\ell_\y,\ell_\z}$ and $E_\ell$ equal to
  the motional energy of a non-interacting atom in motional state
  $\ell$.  The referee correctly recognizes that when $\ell$ is large,
  it indexes the state of a free particle with an asymptotic energy
  $E_\ell\sim\ell^2\equiv\ell_\x^2+\ell_\y^2+\ell_\z^2$.  If spatial
  overlap integrals (e.g.~$K_{\ell m}$) become constant for large
  $\ell,m,n$, the sum above asymptotically takes the form
  \begin{align*}
    \alpha_3^{(3)} \stackrel{?}{\sim}
    \int \f{\d^3\ell~\d^3m~\d^3n}{\p{\ell^2+m^2}\p{\ell^2+n^2}},
  \end{align*}
  which diverges by dimensional analysis.

  The problem with the above argument is that the overlap integral
  $K_{\ell m}$ does not become constant at large $\ell,m$, but rather
  becomes sharply peaked at $\ell\approx m$.  We address and explain
  this point in the following text, which we have appended to section
  III D after Eq.~(32) on page 16:

  \green{Note that although (22) is a loop diagram, the associated
    factors $\alpha_3^{(3)}$ and $\alpha_5^{(3)}$ in $H_3^{(3)}$ are
    finite.  At large $n$, atoms become free particles for which $n$
    essentially indexes discrete momentum states.  These atoms thus
    have an energy which asymptotically scales as
    $E_n\sim n^2\equiv n_\x^2+n_\y^2+n_\z^2$.  Furthermore, the
    oscillatory behavior of atomic wavefunctions with increasing
    motional state indices $\ell,m$ implies that the overlap integral
    $K_{\ell m}$ (and similarly $K^\ell_m$) becomes sharply peaked at
    $\ell\approx m$ as $\ell$ and $m$ get large.  The asymptotic
    behavior of $\alpha_3^{(3)}$ at large $\ell,m,n$ is therefore
    \begin{align*}
      \alpha_3^{(3)}
      \sim \int \f{\d^3\ell~\d^3m~\d^3n}{\p{\ell^2+m^2}\p{\ell^2+n^2}}
      ~\delta\p{\ell-m}\delta\p{\ell-n}
      \sim \int \f{\d^3\ell}{\ell^4}
      \sim \int_{\ell_{\t{min}}}^\infty \f{\d\ell}{\ell^2}
      \sim \f1{\ell_{\t{min}}},
      \tag{33}
    \end{align*}
    where in the last integral we changed to spherical coordinates,
    and $\ell_{\t{min}}^2$ is the minimum value of $\ell^2$ for which
    (i) the energy $E_\ell\sim\ell^2$, and (ii) the integral
    expression in (33) is a good approximation to the corresponding
    sum in (30).  Note that the introduction of $\ell_{\t{min}}$
    amounts to neglecting a finite number of terms in the sum over
    $\ell,m,n$ in (30), whose contribution to the value of
    $\alpha_3^{(3)}$ is finite.  Convergence of $\alpha_5^{(3)}$ is
    similarly guaranteed by the fact that the overlap integral $K_n$
    does not asymptotically grow with increasing $n$, such that
    $\alpha_5^{(3)}$ asymptotically behaves as
    \begin{align*}
      \alpha_5^{(3)} \sim \int \f{\d^3 n}{n^4}
      \sim \int_{n_{\t{min}}}^\infty \f{\d n}{n^2}
      \sim \f1{n_{\t{min}}},
      \tag{34}
    \end{align*}
    where $n_{\t{min}}$ is defined similarly to $\ell_{\t{min}}$.}

  We hope that this new text addresses potential concerns about
  divergences in a satisfactory manner.

\item Concerning the last point:

  \blue{(ii) The referee is a bit familiar with counter terms in
    standard renormalization of field theories like QED. However,
    there it is required that a counter term in each order
    perturbation theory is introduced. In turn, the authors in the
    present manuscript just introduce a single counter term. The
    referee would expect that a careful theoretical manuscript
    properly discusses the regularization and renormalization of the
    theory as well as all diverging diagrams.}

  \label{pt:renormalization}

  We thank the referee for pointing out that our manuscript would
  benefit from a careful explanation of our renormalization scheme.
  Renormalization is a class of techniques, the details of which may
  look different in the context of different field theories; worse
  still, any chosen means to renormalize a field theory is generally
  not unique.

  In order to clarify our introduction and use of counter-terms, we
  have replaced the following text (page 12, line 35):

### 2019-02-08 multi_body_interactions/papers/theory/reviews_NJP/referee_1_response.tex

  \red{The values of these counter-terms are fixed by enforcing that
    $G_X$ is equal to the net two-body interaction
    strength. Diagrammatically, this renormalization condition is
    \begin{align*}
      \substack{
        \shrink{
          \begin{tikzpicture}
            \begin{feynman}
              \vertex (v);
              \vertex[above left = of v] (f1);
              \vertex[below left = of v] (f2);
              \vertex[above right = of v] (f3);
              \vertex[below right = of v] (f4);
              \diagram* {
                (f1) -- (v),
                (f2) -- (v),
                (v) -- (f3),
                (v) -- (f4) };
            \end{feynman}
          \end{tikzpicture}}
        \\ \O(G)}
      + \substack{
        \shrink{
          \begin{tikzpicture}
            \begin{feynman}
              \vertex[crossed dot] (v) {};
              \vertex[above left = of v] (f1);
              \vertex[below left = of v] (f2);
              \vertex[above right = of v] (f3);
              \vertex[below right = of v] (f4);
              \diagram* {
                (f1) -- (v),
                (f2) -- (v),
                (v) -- (f3),
                (v) -- (f4) };
            \end{feynman}
          \end{tikzpicture}}
        \\ \O(\tilde G)}
      - \substack{
        \shrink{
          \begin{tikzpicture}
            \begin{feynman}
              \vertex (v1);
              \vertex[above left = of v1] (f1);
              \vertex[below left = of v1] (f2);
              \vertex[right = of v1] (v2);
              \vertex[above right = of v2] (f3);
              \vertex[below right = of v2] (f4);
              \diagram* {
                (f1) -- (v1),
                (f2) -- (v1),
                (v2) -- (f3),
                (v2) -- (f4),
                (v1) --[scalar, half left] (v2),
                (v1) --[scalar, half right] (v2) };
            \end{feynman}
          \end{tikzpicture}}
        \\ \O(G^2)}
      + \cdots = \substack{
        \shrink{
          \begin{tikzpicture}
            \begin{feynman}
              \vertex (v);
              \vertex[above left = of v] (f1);
              \vertex[below left = of v] (f2);
              \vertex[above right = of v] (f3);
              \vertex[below right = of v] (f4);
              \diagram* {
                (f1) -- (v),
                (f2) -- (v),
                (v) -- (f3),
                (v) -- (f4) };
            \end{feynman}
          \end{tikzpicture}}
        \\ \O(G)}.
      \tag{16}
    \end{align*}
    where we represent counter-terms by a crossed dot (i.e.~$\otimes$)
    at a vertex. To leading order in the coupling constants, it
    follows that the counter-terms are second order in the coupling
    constants, i.e.~$\tilde G\sim G^2$. This finding implies that
    counter-terms only come into play at next- to-leading order (NLO)
    in the calculation of any effective $M$-body interaction
    Hamiltonian.}

  by a new paragraph with more detailed discussion of counter-terms
  and the renormalization condition:

  \green{The introduction of counter-terms is merely a formal
    decomposition of the ``bare'' coupling constants $G_X^{\t{bare}}$
    that are used in (15) as $G_X^{\t{bare}} = G_X + \tilde G_X$.  In
    performing such a decomposition, we are free to choose the values
    of $G_X$, which in turn fixes the values of
    $\tilde G_X \equiv G_X^{\t{bare}} - G_X$.  For convenience, we can
    choose the values of $G_X$ to be those of the physically observed
    effective coupling constants on the right-hand side of (15).
    Representing the new coupling constants $G_X$ by regular vertices
    and the counter-terms $\tilde G_X$ by a crossed dot
    (i.e.~$\otimes$), this choice leads to the {\it renormalization
      condition}
    \begin{align*}
      \substack{
        \shrink{
          \begin{tikzpicture}
            \begin{feynman}
              \vertex (v);
              \vertex[above left = of v] (f1);
              \vertex[below left = of v] (f2);
              \vertex[above right = of v] (f3);
              \vertex[below right = of v] (f4);
              \diagram* {
                (f1) -- (v),
                (f2) -- (v),
                (v) -- (f3),
                (v) -- (f4) };
            \end{feynman}
          \end{tikzpicture}}
        \\ \O(G)}
      + \substack{
        \shrink{
          \begin{tikzpicture}
            \begin{feynman}
              \vertex[crossed dot] (v) {};
              \vertex[above left = of v] (f1);
              \vertex[below left = of v] (f2);
              \vertex[above right = of v] (f3);
              \vertex[below right = of v] (f4);
              \diagram* {
                (f1) -- (v),
                (f2) -- (v),
                (v) -- (f3),
                (v) -- (f4) };
            \end{feynman}
          \end{tikzpicture}}
        \\ \O(\tilde G)}
      - \substack{
        \shrink{
          \begin{tikzpicture}
            \begin{feynman}
              \vertex (v1);
              \vertex[above left = of v1] (f1);
              \vertex[below left = of v1] (f2);
              \vertex[right = of v1] (v2);
              \vertex[above right = of v2] (f3);
              \vertex[below right = of v2] (f4);
              \diagram* {
                (f1) -- (v1),
                (f2) -- (v1),
                (v2) -- (f3),
                (v2) -- (f4),
                (v1) --[scalar, half left] (v2),
                (v1) --[scalar, half right] (v2) };
            \end{feynman}
          \end{tikzpicture}}
        \\ \O(G^2)}
      + \cdots = \substack{
        \shrink{
          \begin{tikzpicture}
            \begin{feynman}
              \vertex (v);
              \vertex[above left = of v] (f1);
              \vertex[below left = of v] (f2);
              \vertex[above right = of v] (f3);
              \vertex[below right = of v] (f4);
              \diagram* {
                (f1) -- (v),
                (f2) -- (v),
                (v) -- (f3),
                (v) -- (f4) };
            \end{feynman}
          \end{tikzpicture}}
        \\ \O(G)}.
      \tag{16}
    \end{align*}
    This renormalization condition has the benefit of allowing us to
    express effective two-body interactions simply in terms of
    physically observed effective two-body coupling constants, rather
    than in terms of long sums at all order of the bare coupling
    constants.}

  We have also added a paragraph explaining where and why counter-term
  diagrams should appear in our effective theory, in particular
  explaining why counter-terms do not appear at leading order for
  effective $M$-body interactions.  This new paragraph is inserted
  between lines 23 and 24 on page 13:

  \green{Second, the renormalization condition in (16) implies that
    the counter terms $\tilde G_X$ are second order in the coupling
    constants $G_X$, i.e.~$\tilde G_X\sim G_X^2$.  Although the
    effective Hamiltonian expansions in (13) and (14) are organized in
    powers of the interaction Hamiltonian $H_{\t{int}}$, the couplings
    $G_X$ are the ``small'' parameters in which we can formally
    organize a perturbation theory; more specifically, the formally
    small quantities organizing our perturbation theory are two-body
    ground-state interaction energies (proportional to the couplings
    $G_X$) divided by the spectral gap of the single-atom Hamiltonian
    $H_0$.  If $M$ atoms can only couple through terms represented by
    a $p$-vertex diagrams for $p\ge p_M^{\t{min}}$, then the leading
    order contribution to $M$-body interactions is order
    $p_M^{\t{min}}$ in the couplings $G_X$.  If the same
    $p_M^{\t{min}}$-vertex diagrams involve any counter-terms,
    however, then these diagrams are at least order $p_M^{\t{min}}+1$
    in the couplings $G_X$.  Counter-terms therefore only appear at
    next-to-leading order (NLO) in the calculation of effective
    $M$-body interactions.}

  To reflect this added paragraph, we have modified the text on page
  13, line 7:

  \red{Before moving on to consider effective three-body interactions,
    there are two comments we must make concerning the result in
    (17).}

  to read:

  \green{Before moving on to consider effective three-body
    interactions, there are a few comments we must make concerning
    renormalization and the result in (17).}

  We also addressed the subject of divergences and the reason for
  their appearance in new text immediately following Eq.~(15) (page
  12), as discussed earlier in point \ref{pt:pseudo-potential}.

  We hope that these changes clarify any confusions about our
  renormalization scheme, and in particular about the appearances (or
  lack thereof) of counter-terms at different orders in our
  perturbative effective theory.

\item Finally:

  \blue{In summary, the manuscript can not be published in the present
    form without strongly improving the readability and in addition
    provide a more detailed analysis of all diverging diagrams and a
    proper discussion of their renormalization.}

  We thank the referee for their extensive and detailed review of our
  manuscript.  The referee brought up many good points, which we have
  addressed by the addition of new discussions and the modification of
  existing text.  In light of these revisions, we hope that the
  referee deems our manuscript suitable for publication.  In
  particular, we hope the referee considers our revised manuscript
  more readable and accessible, with sufficient discussion and
  clarification of the potential confusions and concerns brought up by
  the referee.
